\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-22 exps.tex
exps.tex

HRTCS is the human response system described in
Section~\ref{sec:motivating-example}. AECS (Access and Environmental
Control System) is an application that controls an intelligent room
environment described in~\cite{aecs_ispa}.  The system interacts with
two external timers through input/output signals in order to measure how
long the entrance door to the room is being opened and time the illegal
presence (e.g. intruder) that is being detected. The program has been
modified such that the delay constructs are used instead of external
timers as shown in Figure~\ref{delaycode}. In the original AECS, the
system needed to trigger external timer by emitting the output signal in
order to wait for a specific amount of time (e.g.
\texttt{TimerTriggered} in Figure~\ref{delaycode:a}). When the timer
expires, it notifies back to the system through the input signal
\texttt{TimeOut} which is polled at the \texttt{await} statement. With
the new delay constructs, those timers are not necessary and delays can
be expressed directly in the code as shown in Figure~\ref{delaycode:b}.
\begin{figure}[h!]
	\begin{SubFloat}{\label{delaycode:a}}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\scriptsize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\hspace{1cm}%
	\begin{SubFloat}{\label{delaycode:b}}
		\centering
		\begin{minipage}[b]{0.5\linewidth}
			\scriptsize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(2.4 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}
Motor is a stepper motor controller from~\cite{Bourke2009a}, used for
producing monochrome images on paper by applying a correct application
of current to the print head (a row of resistors). In this example,
duration of current applied to the print head is controlled based on
feedback logic where delays are expressed in real-time Esterel
constructs. We have rewritten the program in SystemJ with our delay
construct and compare between desired and relaxed delay according to
WCRT and BCRT of the program. Printer is an example from [], which
models a printer and a spooler in timed CSP. Their operation is rather
simple: as soon as the spooler receives a print job, passes it to the
printer through channel for processing. The example demonstrates that by
specifying delay bounds (e.g. 1 to 5 time units) between two subsequent
behaviors, the job is passed along the channel as soon as both processes
become ready.

@@

HRTCS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. In this case, as explained previously, delay
statements replaced the external timers and corresponding interface
signals. The system triggers an alarm after 10 seconds of detection of
an intruder or generates a beep sound when an entrance door is being
opened for the same amount of time. For Printer, each spooler and
printer process is mapped to a single clock-domain. Spooler CD sends a
job to the Printer CD between [] to [] ms after receiving it from the
enviornment (e.g. a user). On the other hand, Printer CD notifies
environment that it starts printing between [] to [] ms once it receives
the job from the Spooler CD. Actual print job is started between [] to
[] after the notification. Lastly, Motor is a synchronous program with 5
delay statements where they controls amount of current into the stepper
motor coils.

@@

As one can see in Table \ref{fig:comparison}, BCRT and WCRT were
calculated for all examples. Given the real-time \mbox{\texttt{delay
(M..N)}} provided by programmers, required logical delay \texttt{d} was
determined by applying Algorithm~\ref{alg:1}. In HRTCS, real-time delay
of the range 50.3..200.3 (ms) is only satisfied when \emph{d} is between
1506 and 1787 (as shown previously in
Section~\ref{sec:intr-real-time}~\ref{sec:find-logic-delay}).  It is
then compiler's job to statically choose one of the values in this
range.

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRTCS to obtain a feasible \texttt{d}. Therefore,
Algorithm \ref{alg:2} is applied to those examples, where relaxation was
required, to determine the minimum upper real-time bound \emph{N} such
that there exist a solution for \emph{D} in Algorithm \ref{alg:1}. This
algorithm gives a unique number for logical tick delay \emph{d} such
that \emph{d} = Min(\emph{$S_2$}) = Max(\emph{$S_1$}).  The compiler,
therefore, will choose \emph{d} based on the newly computed \emph{N} for
the examples: Printer, Motor and AECS.

>>>>

HRTCS is the human response system described in
Section~\ref{sec:motivating-example}. AECS (Access and Environmental
Control System) is an application that controls an intelligent room
environment described in~\cite{aecs_ispa}.  The system interacts with
two external timers through input/output signals in order to measure how
long the entrance door to the room is being opened and time the illegal
presence (e.g. intruder) that is being detected. The program has been
modified such that the delay constructs are used instead of external
timers as shown in Figure~\ref{delaycode}. In the original AECS, the
system needed to trigger external timer by emitting the output signal in
order to wait for a specific amount of time (e.g.
\texttt{TimerTriggered} in Figure~\ref{delaycode:a}). When the timer
expires, it notifies back to the system through the input signal
\texttt{TimeOut} which is polled at the \texttt{await} statement. With
the new delay constructs, those timers are not necessary and delays can
be expressed directly in the code as shown in Figure~\ref{delaycode:b}.

\begin{figure}[h!]
	\begin{SubFloat}{\label{delaycode:a}}
		\centering
		\begin{minipage}[b]{0.3\linewidth}
			\scriptsize
\begin{verbatim}
emit TimerTriggered;
trap(T){
  abort(DoorOpened){
    await(TimeOut);
    exit(T); 
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\hspace{1cm}%
	\begin{SubFloat}{\label{delaycode:b}}
		\centering
		\begin{minipage}[b]{0.5\linewidth}
			\scriptsize
\begin{verbatim}
// No emit statement
trap(T){
  abort(DoorOpened){
    delay(2.4 ms);
    exit(T);  
  }
}
\end{verbatim}
		\end{minipage}
	\end{SubFloat}
\caption{Replacing external timer with delay construct}
\label{delaycode}
\end{figure}

Motor is a stepper motor controller from~\cite{Bourke2009a}, used for
producing monochrome images on paper by applying a correct application
of current to the print head (a row of resistors). In this example,
duration of current applied to the print head is controlled based on
feedback logic using real-time delays which are expressed in Esterel
constructs. We have rewritten the program in SystemJ and compared
between desired and relaxed delay according to WCRT and BCRT of the
program.  Printer is an example from [], which models a printer and a
spooler in timed CSP. Their operation is rather simple: as soon as the
spooler receives a print job, passes it to the printer through channel
for processing. The example demonstrates that by specifying delay bounds
(e.g. 1 to 5 time units) between two subsequent behaviors, the job is
passed along the channel as soon as both processes become ready.

@@

HRTCS consists of 2 CDs, but only one with real-time delays. AECS also
has 2 CDs; CD1 consist of a single delay statement, while CD2 has 2
delay statements. In this case, as explained previously, delay
statements replace the external timers and corresponding interface
signals. The system triggers an alarm 10 seconds after detection of an
intruder or generates a beep sound when an entrance door is being opened
for the same amount of time. In Printer, each spooler and printer
process is mapped to a single clock-domain. Spooler CD sends a job to
the Printer CD between [] to [] ms after receiving it from the
enviornment (e.g. a user). On the other hand, Printer CD notifies
environment that it starts printing between [] to [] ms once it receives
the job from the Spooler CD. Actual print job is started between [] to
[] after the notification. In this example, bounded delay ensures that
both channel communication and print job should occur within the
specified amount of time. Lastly, Motor is a synchronous program with 5
delay statements where they controls amount of current into the stepper
motor coils.

@@

%As one can see in Table \ref{fig:comparison}, 
As a first step, BCRT and WCRT were calculated for all examples. Given
the real-time \mbox{\texttt{delay (M..N)}} provided by programmers,
required logical delay \texttt{d} was determined by applying
Algorithm~\ref{alg:1}. In HRTCS, real-time delay of the range
50.3..200.3 (ms) is only satisfied when \emph{d} is between 1506 and
1787 (as shown previously in
Section~\ref{sec:intr-real-time}~\ref{sec:find-logic-delay}).  It is
then compiler's job to statically choose one of the values in this
range.

% The upper bound \texttt{N} needed to be relaxed for all examples other
% than HRTCS to obtain a feasible \texttt{d}. Therefore,
On the other hand, Algorithm \ref{alg:2} is applied to those examples,
where relaxation was required, to determine the minimum upper real-time
bound \emph{N} such that there exist a solution for \emph{D} in
Algorithm \ref{alg:1}. This algorithm gives a unique number for logical
tick delay \emph{d} such that \emph{d} = Min(\emph{$S_2$}) =
Max(\emph{$S_1$}).  The compiler, therefore, will choose \emph{d} based
on the newly computed \emph{N} for the examples: Printer, Motor and
AECS.
